WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2019-03-06 paper/ms.tex
arxiv submitted

\documentclass[12pt,twocolumn,tighten]{aastex62}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}

@@

In what follows, \S~\ref{sec:observations} presents the new TESS
observations, and \S~\ref{sec:timing} describes our timing analysis.
We tried fitting the data with three models: a constant period; a
steadily shrinking period; and a slightly eccentric, precessing orbit.
A constant period can be ruled out\replaced{, but we}{. We} cannot
distinguish between the \replaced{latter two possibilities}{
  possibilities of a decaying orbit, a precessing orbit, and the
  unmodeled possibility of an orbit being gravitationally perturbed by
  an outer companion}.  \replaced{Either possibility}{Any of the three
scenarios} would have interesting implications\replaced{, described in
\S~\ref{sec:implications}}{ (\S~\ref{sec:implications}), and more data
are required for a definitive ruling (\S~\ref{sec:future}).}
Appendix~\ref{sec:verify_tess} considers the possibility that the
WASP-4 timing anomaly is due to an error in timestamps in the TESS
data products.  We found this possibility to be unlikely because none
of the other hot Jupiters we examined show a timing offset with the
same amplitude as was seen for WASP-4.

>>>>

\documentclass[12pt,twocolumn,tighten]{aastex62}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}

@@

In what follows, \S~\ref{sec:observations} presents the new TESS
observations, and \S~\ref{sec:timing} describes our timing analysis.
We tried fitting the data with three models: a constant period; a
steadily shrinking period; and a slightly eccentric, precessing orbit.
A constant period can be ruled out\replaced{, but we}{. We} cannot
distinguish between the\replaced{ latter two possibilities}{
  possibilities of a decaying orbit, a precessing orbit, and the
  unmodeled possibility of an orbit being gravitationally perturbed by
  an outer companion}.  \replaced{Either possibility}{Any of the three
scenarios} would have interesting implications\replaced{, described in
\S~\ref{sec:implications}}{ (\S~\ref{sec:implications}), and more data
are required for a definitive ruling (\S~\ref{sec:future}).}
Appendix~\ref{sec:verify_tess} considers the possibility that the
WASP-4 timing anomaly is due to an error in timestamps in the TESS
data products.  We found this possibility to be unlikely because none
of the other hot Jupiters we examined show a timing offset with the
same amplitude as was seen for WASP-4.
